%-------------------------
% Resume Template
% Author : Orest Tokovenko
% Github : https://github.com/oresttokovenko
% License : MIT
% Type: General Non-Technical
%------------------------

%-------------------------------------------------------------------------------
%                Document & Class
%-------------------------------------------------------------------------------

\documentclass[letterpaper]{resume_config}

% NOTE: <- font size adjustment is available in the resume_config.cls file on the left hand side. ex. \LoadClass[#pt]{article} where # is 10, 11 or 12

% NOTE: If you need to adjust the space between any two lines, use this function: \vspace{#pt} where # is your number. ex. \vspace{-5pt} decreases the space between lines

%-------------------------------------------------------------------------------
%                Resume Starts Here
%-------------------------------------------------------------------------------

\begin{document}


\Header
    {Yadhukrishnan Pankajakshan} % name
    {San Jose, CA} % city, province
    {+1(669)-281-6923} % phone number
    {yadhukrishnanp231099@gmail.com} % email
    {yk2310} % https://linkedin.com/in/_______
    {krishpy99} % https://github.com/________

\section{Summary}
{
    Data science student with a strong foundation in mathematics, data analysis and machine learning, eager to apply skills in real-world projects and contribute to problems that require data-driven insights.
}

%-------------------------------------------------------------------------------
%                Education
%-------------------------------------------------------------------------------

\section{Education}

\EducationExperience
    {Northeastern University} % school name
    {Master of Science in Computer Science} % credential name
    {Sep 2023 - May 2025} % date of graduation
    {San Jose, California} % city, country of school  
    {}
\EducationExperience
    {Anna University} % school name
    {Bachelor of Engineering in Computer Science and Engineering} % credential name
    {Aug 2017 - May 2021} % date of graduation
    {Chennai, India} % city, country of school
    {GPA: 8.42/10}
\vspace{-5pt}

%-------------------------------------------------------------------------------
%                Skills
%-------------------------------------------------------------------------------
\section{Skills}
\Skills{
    \item{\textbf{Programming: }{Python, R, SQL, NoSQL, C, C++, Ruby, Javascript, Java}}\\
    \item{\textbf{Frameworks: }{tensorflow, scikit-learn, pytorch}}\\
    \item{\textbf{Artificial Intelligence: }{neural networks, regression modelling, computer vision, natural language processing}}\\
    \item{\textbf{Data Science: }{mining, scraping, wrangling, modelling, charting \& plotting}}\\
}

%-------------------------------------------------------------------------------
%                Projects
%-------------------------------------------------------------------------------
\section{Projects}
\Project
    {Digitalizing Handwritten Text using AI}{CNN with CTC, RNN, OpenCV}{Oct 2020 - Mar 2021}
    {
        \item {Assessed accuracy ratings for models to fairly compare their effectiveness with multiple models.} 
        \item {Innovated RNN models with depths of over \textbf{20 layers} and CNN models for character recognition.}
        \item {Reached \textbf{90\%} testing accuracy with internal test data. Covered scope for future improvements through improved training data and neural network analysis in subsequent discussions.}
    }
\Project
    {Employability Rating System}{Linear Regression, Python, Flask}{Jan 2020 - Apr 2020}
    {
        \item {Innovated a rating system for resumes weighing multiple factors achieving a testing accuracy of nearly \textbf{78\%.}}
        \item {Built the regression model using resume data from \textbf{1000+ resumes} manually rated by peers and professors.}
    }
\Project
    {Collision Detection of Vehicles in Traffic}{RNN, OpenCV, Object detection}{Sep 2019 - Jan 2020}
    {
        \item {Traffic camera footage and number plate scans of more than \textbf{4,000 vehicles} from more than \textbf{70 angles} were used to simulate collision detection using computer vision.}
        \item {Created a mobile app for law enforcement to track data, record traffic violations, and receive penalty and insurance claim notifications. The app was tested with \textbf{4+ camera feeds} to generate real-time response.}
    }
\vspace{-10pt}

%-------------------------------------------------------------------------------
%              Relevant Coursework
%-------------------------------------------------------------------------------

\section{Coursework}
\begin{SkillsList}{
    \item{Algorithms}
    \item{\href{https://coursera.org/share/60e08a9390dc0ed469da34213f7a9d9c}{Data Representation}}
    \item{Data Management}
    \item{Data Mining}
    \item{Big Data Analytics}
    \item{Artificial Intelligence}
    \item{Engineering Mathematics}
    \item{Statistics \& Probability}
    \item{\href{https://coursera.org/share/b76edb1c16934e4a06f3553c2c4e67b8}{Machine Learning}}
    \item{Database Management}
    \item{Computation Theory}
    \item{Data structures}
}
\end{SkillsList}


%-------------------------------------------------------------------------------
%                Work Experience
%-------------------------------------------------------------------------------

\section{Work Experience}

\WorkExperience
    {Software Development Engineer}{Barclays}{MERN stack, Javascript, Jenkins, Mainframe}{Chennai, India}{Sep 2021 - Aug 2023}
    {
        \item {Automated testing for external synchronization programs helping save over \textbf{\$50,000 annually.}}
        \item {Developed a number of improvements for a DevOps application increasing user impressions by \textbf{100\%}.} 
        \item {Streamlined 10+ processes using Jenkins pipelines for internal usage saving over \textbf{\$1000} on a daily basis.}
        \item {Coded marking algorithms that handles 1,000,000+ transactions with successful testing accuracy of \textbf{100\%}.}
    }

%-------------------------------------------------------------------------------
%                Links
%-------------------------------------------------------------------------------
\section{Relevant Links}
- \curl{https://codeforces.com/profile/sunboy99}{codeforces.com (sunboy99)} 
- \curl{https://leetcode.com/yk_2310/}{leetcode.com (yk\_2310)} 
- \curl{https://www.hackerrank.com/yk_2310}{hackerrank.com (yk-2310)}

\end{document}
%-------------------------------------------------------------------------------
%                Resume Ends Here
%-------------------------------------------------------------------------------