%-------------------------
% Resume Template
% Author : Orest Tokovenko
% Github : https://github.com/oresttokovenko
% License : MIT
% Type: General Non-Technical
%------------------------

%-------------------------------------------------------------------------------
%                Document & Class
%-------------------------------------------------------------------------------

\documentclass[letterpaper]{resume_config}

% NOTE: <- font size adjustment is available in the resume_config.cls file on the left hand side. ex. \LoadClass[#pt]{article} where # is 10, 11 or 12

% NOTE: If you need to adjust the space between any two lines, use this function: \vspace{#pt} where # is your number. ex. \vspace{-5pt} decreases the space between lines

%-------------------------------------------------------------------------------
%                Resume Starts Here
%-------------------------------------------------------------------------------

\begin{document}


\Header
    {Yadhukrishnan Pankajakshan} % name
    {San Jose, CA} % city, province
    {+1(669)-281-6923} % phone number
    {yadhukrishnanp231099@gmail.com} % email
    {yk2310} % https://linkedin.com/in/_______
    {yk-2310} % https://github.com/________
\vspace{-5pt}

%-------------------------------------------------------------------------------
%                Education
%-------------------------------------------------------------------------------

\section{Education}

\EducationExperience
    {Northeastern University} % school name
    {Master of Science in Computer Science} % credential name
    {Sep 2023 - May 2025 \footnotesize{(expected)}} % date of graduation
    {San Jose, California} % city, country of school  

\EducationExperience
    {Anna University} % school name
    {Bachelor of Engineering in Computer Science and Engineering} % credential name
    {Aug 2017 - May 2021} % date of graduation
    {Chennai, India} % city, country of school
\vspace{-15pt}


%-------------------------------------------------------------------------------
%              Relevant Coursework
%-------------------------------------------------------------------------------

\section{Relevant Coursework}
\vspace{-5pt}
\begin{SkillsList}{
    \item{Algorithms}
    \item{\href{https://coursera.org/share/60e08a9390dc0ed469da34213f7a9d9c}{Data Representation}}
    \item{Data Management}
    \item{Data Mining}
    \item{Big Data Analytics}
    \item{Artificial Intelligence}
    \item{Engineering Mathematics}
    \item{Statistics \& Probability}
    \item{\href{https://coursera.org/share/b76edb1c16934e4a06f3553c2c4e67b8}{Machine Learning}}
    \item{Database Management}
    \item{Computation Theory}
    \item{Data structures}
}
\end{SkillsList}

\vspace{-20pt}

%-------------------------------------------------------------------------------
%                Skills
%-------------------------------------------------------------------------------
\section{Skills}
\Skills{
    \item{\textbf{Programming: }{Python, R, SQL, NoSQL, C, C++, Ruby, Javascript, Java}}\\
    \item{\textbf{Frameworks: }{tensorflow, scikit-learn, pytorch}}\\
    \item{\textbf{Artificial Intelligence: }{neural networks, regression modelling, computer vision, natural language processing}}\\
    \item{\textbf{Data Science: }{mining, scraping, wrangling, modelling, charting \& plotting}}\\
}
\vspace{-10pt}

%-------------------------------------------------------------------------------
%                Work Experience
%-------------------------------------------------------------------------------

\section{Work Experience}

\WorkExperience
    {Software Development Engineer}{Barclays}{Chennai, Tamil Nadu, India}{Sep 2021 - Aug 2023}
    {
        \item {\textbf{[JCL, COBOL]}:Automated testing for external synchronization programs helping \textbf{save over \$50,000 annually.}}
        \item {\textbf{[MERN]}: {Developed a number of improvements for a DevOps application by \textbf{more than 1000 peers}.}} 
        \item {\textbf{[Javascript, Jenkins]}: \textbf{Streamlined 10+ processes} using deployment pipelines for internal usage.}
        \item {\textbf{[COBOL, JCL]}: Coded transaction marking algorithms that handles \textbf{over 10000 simultaneous users}.}
    }

\vspace{-10pt}
%-------------------------------------------------------------------------------
%                Projects
%-------------------------------------------------------------------------------
\section{Projects}
\Project
    {Digitalizing Handwritten Text using AI}{CNN with CTC, RNN, OpenCV}{Oct 2020 - Mar 2021}
    {
        \item {\textbf{Assessed accuracy ratings} for models to fairly compare their effectiveness with multiple models.} \item {Innovated \textbf{RNN models with depths of over 20 layers} and CNN models for character recognition.}
        \item {Using internal test data, \textbf{reached 90\% accuracy}. A subsequent discussion also covered scope for future improvements through improved training data and neural network analysis.}
    }
\Project
    {Employability Rating System}{Linear Regression, Python, Flask}{Jan 2020 - Apr 2020}
    {
        \item {Innovated a rating system for resumes weighing multiple factors achieving a \textbf{testing accuracy of nearly 78\%.}}
        \item {Built the regression model using resume data from \textbf{1000+ resumes manually rated by peers and professors.}}
    }
\Project
    {Collision Detection of Vehicles in Traffic}{RNN, OpenCV, Object detection}{Sep 2019 - Jan 2020}
    {
        \item {Traffic camera footage and number plate scans of \textbf{more than 4,000 vehicles from more than 70 angles} were used to simulate collision detection using computer vision.}
        \item {Created a mobile app for law enforcement to track data, record traffic violations, and receive penalty and insurance claim notifications. The app was tested with \textbf{4+ camera feeds} to generate real-time response.}
    }
\Project
    {Detecting pneumonia using chest X-Rays}{CNN, Python, Flask}{Sep 2019 - Jan 2020}
    {
        \item{\textbf{Trained a CNN model with 5000+ images} of chest X-rays to detect pneumonia.}
        \item{Integrated the model with a simple flask application. Finished as \textbf{one of the top 20 submissions} in a national level hackathon.}
    }
\vspace{-10pt}
%-------------------------------------------------------------------------------
%                Achievements
%-------------------------------------------------------------------------------
\section{Programming and Development}
\begin{URLList}[3][3]
    \item{\curl{https://www.codechef.com/users/kennyackerman}{codechef.com (kennyackerman)}}
    \item{\curl{https://codeforces.com/profile/sunboy99}{codeforces.com (sunboy99)}}
    \item{\curl{https://www.codingame.com/profile/4f13f138fbb2c5db0d5bd41c0a5cacf24466393}{codingame.com}}
    \item{\curl{https://leetcode.com/yk_2310/}{leetcode.com (yk\_2310)}}
    \item{\curl{https://www.coursera.org/user/bc3974bf3f28063b37ad8733c91e6bc1}{coursera.com}}
    \item{\curl{https://www.hackerrank.com/yk_2310}{hackerrank.com (yk-2310)}}
\end{URLList}

\end{document}
%-------------------------------------------------------------------------------
%                Resume Ends Here
%-------------------------------------------------------------------------------