%-------------------------
% Resume Template
% Author : Orest Tokovenko
% Github : https://github.com/oresttokovenko
% License : MIT
% Type: General Non-Technical
%------------------------

%-------------------------------------------------------------------------------
%                Document & Class
%-------------------------------------------------------------------------------

\documentclass[letterpaper]{resume_config}

% NOTE: <- font size adjustment is available in the resume_config.cls file on the left hand side. ex. \LoadClass[#pt]{article} where # is 10, 11 or 12

% NOTE: If you need to adjust the space between any two lines, use this function: \vspace{#pt} where # is your number. ex. \vspace{-5pt} decreases the space between lines

%-------------------------------------------------------------------------------
%                Resume Starts Here
%-------------------------------------------------------------------------------

\begin{document}

\Header
    {Yadhukrishnan Pankajakshan} % name
    {San Jose, CA} % city, province
    {+1(669)-281-6923} % phone number
    {yadhukrishnanp231099@gmail.com} % email
    {yk2310} % https://linkedin.com/in/_______
    {yk-2310}
\vspace{-10pt}
%-------------------------------------------------------------------------------
%                Education
%-------------------------------------------------------------------------------

\section{Education}

\EducationExperience
    {Northeastern University} % school name
    {Master of Science in Computer Science} % credential name
    {Sep 2023 - May 2025 \footnotesize{(expected)}} % date of graduation
    {San Jose, California} % city, country of school  

\EducationExperience
    {Anna University} % school name
    {Bachelor of Engineering in Computer Science and Engineering} % credential name
    {Aug 2017 - May 2021} % date of graduation
    {Chennai, India} % city, country of school
\vspace{-15pt}


%-------------------------------------------------------------------------------
%                Skills
%-------------------------------------------------------------------------------
\section{Skills}
\textbf{Programming: }{Javascript, Java, Python, C, C++, SQL, NoSQL, Typescript, Ruby, Kotlin, R}\\
\textbf{Frameworks: }{ReactJS, expressJS, Rails, Flask, Django, Spring}\\
\textbf{Development Tools: }{Visual Studio Code, IntelliJ}\\
\textbf{Testing and deployment: }{Sonarqube, Google Cloud Platform, Jenkins, Version control(Git)}\\
\textbf{Others: }{Microsoft Office, LaTeX}\\
\vspace{-10pt}

%-------------------------------------------------------------------------------
%              Relevant Coursework
%-------------------------------------------------------------------------------

\section{Relevant Coursework}
\vspace{-5pt}
\begin{SkillsList}{
    \item{O-O Principles}
    \item{Data Structures}
    \item{Algorithms}
    \item{Database Management}
    \item{Operating Systems}
    \item{Software Engineering}
    \item{Computer Networks}
    \item{Mobile Computing}
    \item{Cloud Computing}
    \item{Internet Programming}
    \item{Human Computer Interaction}
}
\end{SkillsList}

\vspace{-20pt}

%-------------------------------------------------------------------------------
%                Work Experience
%-------------------------------------------------------------------------------

\section{Work Experience}

\WorkExperience
    {Software Development Engineer}{Barclays}{ReactJS, ExpressJS, Jenkins, JCL}{Sep 2022 - Aug 2023}
    {
        \item{Automated testing for external synchronization programs helping \textbf{save over \$50,000 annually.}}
        \item {Worked on optimizing log retrieval for a devops application and achieved an \textbf{efficiency boost of 200\%}.}
        \item {Developed a number of improvements for a DevOps application by \textbf{more than 1000 peers}.} 
        \item {\textbf{Streamlined 10+ processes} using deployment pipelines for internal usage.}
    }
\WorkExperience
    {Graduate Analyst}{Barclays}{COBOL, JCL, VSCode, Sonarqube}{Sep 2021 - Aug 2022}
    {
        \item {Coded transaction marking algorithms that handles \textbf{over 10000 simultaneous users}.}
        \item {Created programs for formatting and correcting transaction files with \textbf{1000+ lines} passed to internal systems.}
        \item {Assisted in testing developer tools like Visual studio code and sonarqube for development and code coverage testing \textbf{helping coworkers across India} involved in mainframe development.}
    }
\WorkExperience
    {Software Development Intern}{Tesark Technologies}{Ruby, Rails, Javascript}{Dec 2019 - Jan 2020}
    {
        \item {Developed a \textbf{fully functional library system} as part of learning curve for Ruby on Rails as a framework.}
        \item {Worked on a feature for scheduling tasks for employees in an internal application.}
    }
\vspace{-10pt}
%-------------------------------------------------------------------------------
%                Projects
%-------------------------------------------------------------------------------
\section{Projects}
\Project
    {\href{https://github.com/yk-2310/Social-app}{Social Media Application}}{ReactJS, Redux, MaterialUI, ExpressJS}{Jan 2020 - Mar 2020}
    {
        \item {Built a functional social media application as part of learning React and Express frameworks.}
        \item {Integrated the application using a cloud backend by connecting the entire application to a firebase database.}
    }
\Project
    {\href{https://github.com/yk-2310/Employability-Rating-System-using-Flask}{Employability Rating System}}{Python, flask, Linear Regression}{Sep 2020 - Dec 2020}
    {
        \item {Created a simple front end for a file submission to submit resume. Used a trained (by myself) machine learning model to develop resume ratings and integrated to the flask front-end.}
    }
\Project
    {\href{https://github.com/yk-2310/Blog-Application}{Blog Application}}{Python, flask, SQLite3}{Oct 2019 - Nov 2019}
    {
        \item {Created a simple blog application that allowed users to post blogs and other users to react and comment.}
        \item {Developed it using Python and Flask and integrated it to SQLite3 database.}
    }
\vspace{-10pt}
%-------------------------------------------------------------------------------
%                Achievements
%-------------------------------------------------------------------------------
\section{Programming and Development}
\begin{URLList}[3][3]
    \item{\curl{https://www.codechef.com/users/kennyackerman}{codechef.com (kennyackerman)}}
    \item{\curl{https://codeforces.com/profile/sunboy99}{codeforces.com (sunboy99)}}
    \item{\curl{https://www.codingame.com/profile/4f13f138fbb2c5db0d5bd41c0a5cacf24466393}{codingame.com}}
    \item{\curl{https://leetcode.com/yk_2310/}{leetcode.com (yk\_2310)}}
    \item{\curl{https://www.coursera.org/user/bc3974bf3f28063b37ad8733c91e6bc1}{coursera.com}}
    \item{\curl{https://www.hackerrank.com/yk_2310}{hackerrank.com (yk-2310)}}
\end{URLList}

\end{document}
%-------------------------------------------------------------------------------
%                Resume Ends Here
%-------------------------------------------------------------------------------